Cola report
==================

**Date**: `r Sys.Date()`

----------------------------------------------------------------

<style type='text/css'>
<%
css = paste(readLines(paste0(TEMPLATE_DIR, "/custom.css")), collapse = "\n") -%>
<%= css %>
</style>

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(markdown)
options(markdown.HTML.options = setdiff(c(getOption("markdown.HTML.options"), "toc"), "base64_images"))
options(width = 100)
options(digits = 3)
opts_chunk$set(
	comment = "#>",
	fig.path = "figure_cola/",
	warning = FALSE,
	message = FALSE
)
suppressPackageStartupMessages(library(ComplexHeatmap))
suppressPackageStartupMessages(library(genefilter))
```


<% res_list = object -%>

## Summary

<% same_var_name = var_name == "res_list" -%>

<% if(!same_var_name) { -%>

First the variable name is changed to `res_list`.

```{r, eval = FALSE, echo = TRUE}
res_list = <%=var_name%>
```
<% } -%>

```{r, echo = FALSE}
res_list = object
```

All available functions which can be applied to this `res_list` object:

```{r}
res_list
```

The call of `run_all_consensus_partition_methods()` was:

```{r, echo = FALSE}
print(res_list@calling)
```

Dimension of the input matrix:

```{r}
mat = get_matrix(res_list)
dim(mat)
```

The density distribution for each sample is visualized as heatmap as one column in follwing plot:

```{r, echo = FALSE, message = FALSE}
message(qq("* making density heatmap of global distribution in each sample (@{ncol(mat)} samples)"))
```

```{r density-heatmap}
library(ComplexHeatmap)
<% if(is.null(get_anno(res_list))) { -%>
densityHeatmap(mat, ylab = "value", cluster_columns = TRUE)
<% } else { -%>
densityHeatmap(mat, top_annotation = HeatmapAnnotation(df = get_anno(res_list), 
	col = get_anno_col(res_list)), ylab = "value", cluster_columns = TRUE)
<% } -%>
```

```{r, echo = FALSE, message = FALSE}
n_top_value_method = length(res_list@top_value_method)
n_partition_method = length(res_list@partition_method)
n_method = n_top_value_method * n_partition_method
message(qq("* top rows are extracted by '@{paste(res_list@top_value_method, collapse = ', ')}' methods"))
message(qq("* subgroups are detected by '@{paste(res_list@partition_method, collapse = ', ')}' methods"))
message(qq("  - in total @{n_method} combinations of methods"))
```

`res_list` contains results for 	

```{r, echo = FALSE, message = FALSE}
t1 = Sys.time()
message("* guessing best k for each method", appendLF = FALSE)
```

Best `k` (number of partitions) for each combination of top value methods and partition methods:

```{r, eval = FALSE}
guess_best_k(res_list)
```

```{r, echo = FALSE}
tb = guess_best_k(res_list)
g = expand.grid(res_list@partition_method, res_list@top_value_method)
g = paste0(g[, 2], ":", g[, 1])
od = sapply(rownames(tb), function(x) which(g == x))
rownames(tb) = paste0("[", rownames(tb), "](#toc_", od + 2, ")")
kable(tb)
```

```{r, echo = FALSE}
fs = min(c(3*n_top_value_method, 14))/n_partition_method
```

CDF of consensus matrix for all methods:

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making empirical cumulative distribution curves for all methods"), appendLF = FALSE)
```

```{r collect-plots, fig.width = fs*n_partition_method, fig.height = fs*n_top_value_method, results = "hide"}
collect_plots(res_list, fun = plot_ecdf)
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making consensus heatmaps for all methods"), appendLF = FALSE)
```

Consensus heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% all_k = res_list@list[[1]]@k
fs = min(c(3*length(res_list@top_value_method), 14))/length(res_list@top_value_method)
n_top_value_method = length(res_list@top_value_method)
n_partition_method = length(res_list@partition_method)
n_method = n_top_value_method * n_partition_method
for(k in all_k) { -%>
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message("  - consensus heamtaps for all methods (k = <%=k%>)", appendLF = FALSE)
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = consensus_heatmap)', 'k = <%=k%>', opt = 'fig.width = <%=fs*n_partition_method%>, fig.height = <%=fs*n_top_value_method%>, results = "hide"')
<% } -%>
knitr_insert_tabs()
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making membership heatmaps for all methods"), appendLF = FALSE)
```

Membership heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message("  - membership heamtap for all methods (k = <%=k%>)", appendLF = FALSE)
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = membership_heatmap)', 'k = <%=k%>', opt = 'fig.width =<%=fs*n_partition_method%>, fig.height = <%=fs*n_top_value_method%>, results = "hide"')
<%}-%>
knitr_insert_tabs()
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* making signature heatmaps for all methods"), appendLF = FALSE)
```

Signature heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message("  - signature heamtap for all methods (k = <%=k%>)", appendLF = FALSE)
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = get_signatures)', 'k = <%=k%>', opt = 'fig.width = <%=fs*n_partition_method%>, fig.height = <%=fs*n_top_value_method%>, results = "hide"')
<%}-%>
knitr_insert_tabs()
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* getting statistics for all methods"), appendLF = FALSE)
```

Get statistics for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('get_stat(res_list, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```


```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* collecting classifications for all methods"), appendLF = FALSE)
```

Collect partitions from all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message("  - classifications from all methods (k = <%=k%>)", appendLF = FALSE)
knitr_add_tab_item('collect_classes(res_list, k = <%=k%>)', 'k = <%=k%>', opt = 'fig.width = 8, fig.height = 8')
<%}-%>
knitr_insert_tabs()
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* overlaping top rows from different top value methods"), appendLF = FALSE)
```

Overlap of top rows in different top methods:

<% oe = try(loadNamespace("venneuler"), silent = TRUE)
if(inherits(oe, "try-error")) {
   venn_method = "venn"
} else {
   venn_method = "venneuler"
}-%>

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(top_n in res_list@list[[1]]@top_n) { -%>
knitr_add_tab_item('top_rows_overlap(res_list, top_n = <%=top_n%>, method = "<%=venn_method%>")', 'top_n = <%=top_n%>', opt = 'fig.width = 5, fig.height = 5')
<%}-%>
knitr_insert_tabs()
```

Also visualize the correspondance of rankings between different top methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(top_n in res_list@list[[1]]@top_n) { -%>
knitr_add_tab_item('top_rows_overlap(res_list, top_n = <%=top_n%>, method = "correspondance")', 'top_n = <%=top_n%>', opt = 'fig.width = 14, fig.height = 8')
<%}-%>
knitr_insert_tabs()
```

Heatmaps for the top rows:

<% 
n_top_value_method = length(res_list@top_value_method)
if(n_top_value_method <= 4) {
	fig_width = 14/4 * n_top_value_method
	fig_height = 14/4
} else {
	fig_width = 14
	fig_height = 14/n_top_value_method
}
-%>

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(top_n in res_list@list[[1]]@top_n) { -%>
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message("  - comparing top row methods by heatmap (top_n = <%=top_n%>)", appendLF = FALSE)
knitr_add_tab_item('top_rows_heatmap(res_list, top_n = <%=top_n%>)', 'top_n = <%=top_n%>', opt = 'fig.width = <%=fig_width%>, fig.height = <%=fig_height%>')
<%}-%>
knitr_insert_tabs()
```

<% has_known_anno = FALSE
if(!is.null(res_list@list[[1]]@anno)) { 
has_known_anno = TRUE -%>


```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1)))); t1 = Sys.time()
message(qq("* testing correlation of subgroups to known annotations"), appendLF = FALSE)
```

Test correlation between subgroups and known annotations:

```{r, results = 'asis', echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('test_to_known_factors(res_list, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

```{r, echo = FALSE, message = FALSE}
t2 = Sys.time(); message(paste0(", ", gsub("^ +", "", format(t2 - t1))));
```

<%}-%> 

## Results for each method

<% 
is_hc = FALSE
n_section = n_top_value_method * n_partition_method
i_section = 0
for(top_value_method in res_list@top_value_method) {
    for(partition_method in res_list@partition_method) { 
    	i_section = i_section + 1 -%>
    	<% brew(paste0(TEMPLATE_DIR, "/section_template.Rmd")) %>

<% }} -%>

## Session info

```{r}
sessionInfo()
```

```{r, echo = FALSE, message = FALSE}
message("-----------------------------------------------------------------")
```
