Cola report
==================

**Date**: `r Sys.Date()`

----------------------------------------------------------------

<style type='text/css'>
<%
extdata_dir = "~/project/cola/inst/extdata";
css = paste(readLines(paste0(extdata_dir, "/custom.css")), collapse = "\n") -%>
<%= css %>
</style>

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(markdown)
options(markdown.HTML.options = setdiff(c(getOption("markdown.HTML.options"), "toc"), "base64_images"))
options(width = 100)
opts_chunk$set(
	comment = "#>",
	fig.path = "figure_cola/",
	warning = FALSE,
	message = FALSE
)
```

## Summary

All available functions which can be applied to `res_list` object.

<% same_var_name = var_name == "res_list" -%>

```{r, eval = <%= ifelse(same_var_name, '1:2','2:3')%>, echo = <%= ifelse(same_var_name, '2', 'c(1, 3)')%>}
<% if(!same_var_name) { -%>
res_list = <%=var_name%>
<% } -%>
res_list = object
res_list
```

The call for `run_all_consensus_partition_methods()`:

```{r, echo = FALSE}
print(res_list@call)
```

Dimension of the input matrix:

```{r}
dim(res_list@.env$data)
```

Global distribution for each sample:

```{r density-heatmap}
library(ComplexHeatmap)
<% if(is.null(res_list@list[[1]]@known_anno)) { -%>
densityHeatmap(res_list@.env$data, ylab = "value")
<% } else { -%>
densityHeatmap(res_list@.env$data, anno = HeatmapAnnotation(df = res_list@list[[1]]@known_anno, 
	col = res_list@list[[1]]@known_col), ylab = "value")
<% } -%>
```

Best `k` (number of partitions) for each combination of top methods and partition methods.

```{r, eval = FALSE}
get_best_k(res_list)
```

```{r, echo = FALSE}
tb = get_best_k(res_list)
kable(tb)
```

```{r, echo = FALSE}
fs = min(c(3*length(res_list@top_method), 14))/length(res_list@top_method)
n_top_method = length(res_list@top_method)
n_partition_method = length(res_list@partition_method)
```


CDF of consensus matrix for all methods:

```{r collect-plots, fig.width = fs*n_top_method, fig.height = fs*n_partition_method}
collect_plots(res_list, fun = plot_ecdf)
```

Consensus heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% all_k = res_list@list[[1]]@k
fs = min(c(3*length(res_list@top_method), 14))/length(res_list@top_method)
n_top_method = length(res_list@top_method)
n_partition_method = length(res_list@partition_method)
for(k in all_k) { -%>
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = consensus_heatmap)', 'k = <%=k%>', opt = 'fig.width = <%=fs*n_top_method%>, fig.height = <%=fs*n_partition_method%>')
<% } -%>
knitr_insert_tabs()
```


Membership heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = membership_heatmap)', 'k = <%=k%>', opt = 'fig.width =<%=fs*n_top_method%>, fig.height = <%=fs*n_partition_method%>')
<%}-%>
knitr_insert_tabs()
```

Signature heatmaps for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('collect_plots(res_list, k = <%=k%>, fun = get_signatures)', 'k = <%=k%>', opt = 'fig.width = <%=fs*n_top_method%>, fig.height = <%=fs*n_partition_method%>')
<%}-%>
knitr_insert_tabs()
```

Get statistics for all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('get_stat(res_list, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

Collect partitions from all methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('collect_classes(res_list, k = <%=k%>)', 'k = <%=k%>', opt = 'fig.width = 14, fig.height = 8')
<%}-%>
knitr_insert_tabs()
```

Overlap of top rows in different top methods:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(top_n in res_list@list[[1]]@top_n) { -%>
knitr_add_tab_item('top_rows_overlap(res_list, top_n = <%=top_n%>)', 'top_n = <%=top_n%>', opt = 'fig.width = 5, fig.height = 5')
<%}-%>
knitr_insert_tabs()
```

Also visualize the correspondance of rankings between different top methods:

```{r top-row-overlap, fig.width = 14, fig.height = 8}
top_rows_overlap(res_list, top_n = <%= min(res_list@list[[1]]@top_n) %>, type = "correspondance")
```

Heatmaps for the top rows:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(top_n in res_list@list[[1]]@top_n) { -%>
knitr_add_tab_item('top_rows_heatmap(res_list, top_n = <%=top_n%>)', 'top_n = <%=top_n%>', opt = 'fig.width = 14, fig.height = 14/<%=length(res_list@list[[1]]@top_n)%>')
<%}-%>
knitr_insert_tabs()
```

<% if(!is.null(res_list@list[[1]]@known_anno)) { -%>

Test correlation between subgroups and known annotations:

```{r, results = 'asis', echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('test_to_known_factors(res_list, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

<%}-%> 

## Results for each method

<% 
is_hc = FALSE
for(top_method in res_list@top_method) {
    for(partition_method in res_list@partition_method) { -%>

        <% brew(paste0(extdata_dir, "/section_template.Rmd")) %>

<% }} -%>

## Session info

```{r}
sessionInfo()
```
