Cola report
==================

**Date**: `r Sys.Date()`

----------------------------------------------------------------


<style type='text/css'>
#toc {
  position: fixed;
  left: 0;
  top: 20px;
  width: 200px;
  height: 100%;
  overflow:auto;
  padding: 0px 10px 0px 10px;
}
#toc_header {
  display: none;
}
#toc ul {
  margin: 0px;
  padding: 0px;
}
#toc ul li {
  list-style-type: none;
}

#toc ul li ul li {
  margin-left: 15px;
  list-style-type: circle;
}
body, td {
   font-family: Arial,Helvetica,sans-serif;
   background-color: white;
   font-size: 13px;
  max-width: 800px;
  margin: auto;
  margin-left:210px;
  padding: 0px 10px 0px 10px;
  border-left: 1px solid #EEEEEE;
  line-height: 150%;
}

tt, code, pre {
   font-family: 'DejaVu Sans Mono', 'Droid Sans Mono', 'Lucida Console', Consolas, Monaco, 

monospace;
}

h1 {
   font-size:2.2em;
}

h2 {
   font-size:1.8em;
}

h3 {
   font-size:1.4em;
}

h4 {
   font-size:1.0em;
}

h5 {
   font-size:0.9em;
}

h6 {
   font-size:0.8em;
}

a {
  text-decoration: none;
}

a:hover {
  text-decoration: underline;
}

a:visited {
   color: rgb(50%, 0%, 50%);
}

pre, img {
  max-width: 100%;
}
pre {
  overflow-x: auto;
}
pre code {
   display: block; padding: 0.5em;
}

code {
  font-size: 92%;
  border: 1px solid #ccc;
}

code[class] {
  background-color: #F8F8F8;
}

table, td, th {
  border: none;
}

blockquote {
   color:#666666;
   margin:0;
   padding-left: 1em;
   border-left: 0.5em #EEE solid;
}

hr {
   height: 0px;
   border-bottom: none;
   border-top-width: thin;
   border-top-style: dotted;
   border-top-color: #999999;
}

@media print {
   * {
      background: transparent !important;
      color: black !important;
      filter:none !important;
      -ms-filter: none !important;
   }

   body {
      font-size:12pt;
      max-width:100%;
   }

   a, a:visited {
      text-decoration: underline;
   }

   hr {
      visibility: hidden;
      page-break-before: always;
   }

   pre, blockquote {
      padding-right: 1em;
      page-break-inside: avoid;
   }

   tr, img {
      page-break-inside: avoid;
   }

   img {
      max-width: 100% !important;
   }

   @page :left {
      margin: 15mm 20mm 15mm 10mm;
   }

   @page :right {
      margin: 15mm 10mm 15mm 20mm;
   }

   p, h2, h3 {
      orphans: 3; widows: 3;
   }

   h2, h3 {
      page-break-after: avoid;
   }
}
</style>

```{r, echo = FALSE, message = FALSE}
library(markdown)
options(markdown.HTML.options = c(options('markdown.HTML.options')[[1]], "toc"))
options(width = 100)
```

```{r, echo = FALSE}
library(GetoptLong)
KNITR_TAB_ENV = environment()
KNITR_TAB_ENV$current_tab_index = 0
KNITR_TAB_ENV$header = NULL
KNITR_TAB_ENV$current_html = ""
KNITR_TAB_ENV$random_str = runif(1, min = 1, max = 1e8)
KNITR_TAB_ENV$css_added = FALSE
knitr_add_tab_item = function(code, header, desc ="") {
	KNITR_TAB_ENV$current_tab_index = KNITR_TAB_ENV$current_tab_index + 1
	tab = qq("tab-@{KNITR_TAB_ENV$random_str}-@{KNITR_TAB_ENV$current_tab_index}")
	knitr_text = qq(
"@{strrep('`', 3)}{r @{tab}}
@{code}
@{strrep('`', 3)}

@{desc}
")	
	md = knit(text = knitr_text, quiet = TRUE)
	html = markdownToHTML(text = md, fragment.only = TRUE)
	html = qq("<div id='@{tab}'>\n@{html}\n</div>\n")
	
	KNITR_TAB_ENV$header = c(KNITR_TAB_ENV$header, header)
	KNITR_TAB_ENV$current_html = paste0(KNITR_TAB_ENV$current_html, html)
	return(invisible(NULL))
}

knitr_insert_tabs = function() {
	if(!KNITR_TAB_ENV$css_added) {
		css = readLines("https://code.jquery.com/ui/1.12.1/themes/base/jquery-ui.css")
		cat("<style type='text/css'>\n")
		cat(css, sep = "\n")
		cat("</style>\n")
	}
	cat("
<script src='https://code.jquery.com/jquery-1.12.4.js'></script>
<script src='https://code.jquery.com/ui/1.12.1/jquery-ui.js'></script>
<script>
$( function() {
	$( '#tabs' ).tabs();
} );
</script>
")
	cat("<div id='tabs'>\n")
	cat("<ul>\n")
	qqcat("<li><a href='#tab-@{KNITR_TAB_ENV$random_str}-@{seq_len(KNITR_TAB_ENV$current_tab_index)}'>@{KNITR_TAB_ENV$header}</a></li>\n")
	cat("</ul>\n")
	cat(KNITR_TAB_ENV$current_html)
	cat("</div>\n")

	KNITR_TAB_ENV$current_tab_index = 1
	KNITR_TAB_ENV$header = NULL
	KNITR_TAB_ENV$current_html = ""
	KNITR_TAB_ENV$random_str = runif(1, min = 1, max = 1e8)
	KNITR_TAB_ENV$css_added = TRUE
	
	return(invisible(NULL))
}
```



All available functions which can be applied to `res_list` object.

```
res_list
```

```{r}
get_best_k(res_list)
```

Collect all plots for a k:

```{r, fig.width = 14, fig.height = 14*length(all_top_value_methods())/length(all_partition_methods()), results = "hide"}
collect_plots(res_list, k = 4, fun = plot_ecdf)
collect_plots(res_list, k = 4, fun = consensus_heatmap)
collect_plots(res_list, k = 4, fun = membership_heatmap)
# collect_plots(res_list, k = 3, fun = get_signatures)
```

```{r}
get_stat(res_list, k = 4)
```

```{r, fig.width = 12}
collect_classes(res_list, k = 4)
```

Overlap of top rows in different top methods:

[% 
n_top = res_list@list[[1]]@top_n
n_top_nc = min(c(3, length(n_top)))
n_top_nr = ceiling(length(n_top)/n_top_nc)
"" %]

```{r, fig.width = 14, fig.height = 14/3}
par(mfrow = c([% n_top_nr %], [% n_top_nc %]))
[% paste("top_rows_overlap(res_list, top_n = ", n_top, ")", sep = "", collapse = "\n") %]
```

Also visualize the correspondance of rankings between different scoreing methods:

```{r, fig.width = 14, fig.height = 8}
top_rows_overlap(res_list, top_n = [% min(n_top) %], type = "correspondance")
```

Heatmaps for the top rows:

```{r, fig.width = 14, fig.height = 14/4}
top_rows_heatmap(res_list, top_n = [% min(n_top) %])
```


[% 
section_template = paste(readLines("~/project/cola/inst/extdata/section_template.Rmd"), collapse = "\n")
section = NULL
for(top_method in res_list@top_method) {
    for(partition_method in res_list@partition_method) {
        section = c(section, qq(section_template))
    }
}
section = c(section, "\n")
paste(section, collapse = "\n\n") %]


## Session info

```{r}
sessionInfo()
```
