Cola report
==================

**Date**: `r Sys.Date()`

----------------------------------------------------------------


<style type='text/css'>
#toc {
  position: fixed;
  left: 0;
  top: 20px;
  width: 200px;
  height: 100%;
  overflow:auto;
  padding: 0px 10px 0px 10px;
}
#toc_header {
  display: none;
}
#toc ul {
  margin: 0px;
  padding: 0px;
}
#toc ul li {
  list-style-type: none;
}

#toc ul li ul li {
  margin-left: 15px;
  list-style-type: circle;
}
body, td {
   font-family: Arial,Helvetica,sans-serif;
   background-color: white;
   font-size: 13px;
  max-width: 800px;
  margin: auto;
  margin-left:210px;
  padding: 0px 10px 0px 10px;
  border-left: 1px solid #EEEEEE;
  line-height: 150%;
}

tt, code, pre {
   font-family: 'DejaVu Sans Mono', 'Droid Sans Mono', 'Lucida Console', Consolas, Monaco, 

monospace;
}

h1 {
   font-size:2.2em;
}

h2 {
   font-size:1.8em;
}

h3 {
   font-size:1.4em;
}

h4 {
   font-size:1.0em;
}

h5 {
   font-size:0.9em;
}

h6 {
   font-size:0.8em;
}

a {
  text-decoration: none;
}

a:hover {
  text-decoration: underline;
}

a:visited {
   color: rgb(50%, 0%, 50%);
}

pre, img {
  max-width: 100%;
}
pre {
  overflow-x: auto;
}
pre code {
   display: block; padding: 0.5em;
}

code {
  font-size: 92%;
  border: 1px solid #ccc;
}

code[class] {
  background-color: #F8F8F8;
}

table, td, th {
  border: none;
}

blockquote {
   color:#666666;
   margin:0;
   padding-left: 1em;
   border-left: 0.5em #EEE solid;
}

hr {
   height: 0px;
   border-bottom: none;
   border-top-width: thin;
   border-top-style: dotted;
   border-top-color: #999999;
}

@media print {
   * {
      background: transparent !important;
      color: black !important;
      filter:none !important;
      -ms-filter: none !important;
   }

   body {
      font-size:12pt;
      max-width:100%;
   }

   a, a:visited {
      text-decoration: underline;
   }

   hr {
      visibility: hidden;
      page-break-before: always;
   }

   pre, blockquote {
      padding-right: 1em;
      page-break-inside: avoid;
   }

   tr, img {
      page-break-inside: avoid;
   }

   img {
      max-width: 100% !important;
   }

   @page :left {
      margin: 15mm 20mm 15mm 10mm;
   }

   @page :right {
      margin: 15mm 10mm 15mm 20mm;
   }

   p, h2, h3 {
      orphans: 3; widows: 3;
   }

   h2, h3 {
      page-break-after: avoid;
   }
}
</style>

```{r, echo = FALSE, message = FALSE}
library(markdown)
options(markdown.HTML.options = unique(c(options('markdown.HTML.options')[[1]], "toc")))
options(markdown.HTML.options = setdiff(op, "base64_images"))
options(width = 100)
opts_chunk$set(comment = "#>")
```

All available functions which can be applied to `res_list` object.

```{r}
res_list
```

```{r}
get_best_k(res_list)
```

Collect all plots for a k:

```{r consensus-partition-list-collect-plots, fig.width = 14, fig.height = 14*length(all_top_value_methods())/length(all_partition_methods()), results = "hide"}
collect_plots(res_list, k = 2, fun = plot_ecdf)
collect_plots(res_list, k = 2, fun = consensus_heatmap)
collect_plots(res_list, k = 2, fun = membership_heatmap)
# collect_plots(res_list, k = 3, fun = get_signatures)
```

```{r, results = "asis", echo = FALSE, include = TRUE}
[% k = res_list@list[[1]]@k
qq("knitr_add_tab_item(\"get_stat(res_list, k = @<k>)\", \"k = @<k>\")\n", code.pattern = "@<CODE>") %]
knitr_insert_tabs()
```

```{r consensus-partition-list-collect-classes, results = "asis", echo = FALSE, include = TRUE}
[% k = res_list@list[[1]]@k
qq("knitr_add_tab_item(\"collect_classes(res_list, k = @<k>)\", \"k = @<k>\")\n", code.pattern = "@<CODE>") %]
knitr_insert_tabs()
```

Overlap of top rows in different top methods:

[% 
n_top = res_list@list[[1]]@top_n
n_top_nc = min(c(3, length(n_top)))
n_top_nr = ceiling(length(n_top)/n_top_nc)
"" %]

```{r top-row-overlap, fig.width = 14, fig.height = 14/3}
par(mfrow = c([% n_top_nr %], [% n_top_nc %]))
[% paste("top_rows_overlap(res_list, top_n = ", n_top, ")", sep = "", collapse = "\n") %]
```

Also visualize the correspondance of rankings between different scoreing methods:

```{r top-row-overlap-by-correspondance, fig.width = 14, fig.height = 8}
top_rows_overlap(res_list, top_n = [% min(n_top) %], type = "correspondance")
```

Heatmaps for the top rows:

```{r top-row-heatmap, fig.width = 14, fig.height = 14/4}
top_rows_heatmap(res_list, top_n = [% min(n_top) %])
```


[% 
section_template = paste(readLines("~/project/cola/inst/extdata/section_template.Rmd"), collapse = "\n")
section = NULL
for(top_method in res_list@top_method) {
    for(partition_method in res_list@partition_method) {
        section = c(section, qq(section_template))
    }
}
section = c(section, "\n")
paste(section, collapse = "\n\n") %]


## Session info

```{r}
sessionInfo()
```
