Cola report for hierarchical partitioning
==================

**Date**: `r Sys.Date()`

----------------------------------------------------------------

<style type='text/css'>
<%
extdata_dir = "~/project/cola/inst/extdata";
css = paste(readLines(paste0(extdata_dir, "/custom.css")), collapse = "\n") -%>
<%= css %>
</style>

```{r, echo = FALSE, message = FALSE}
library(markdown)
options(markdown.HTML.options = setdiff(c(getOption("markdown.HTML.options"), "toc"), "base64_images"))
options(width = 100)
opts_chunk$set(comment = "#>")
opts_chunk$set(fig.path = "figure_hc/")
```

## Summary

All available functions which can be applied to `res` object.

```{r}
<% if(var_name != "res_hc") { -%>
res_hc = <%=var_name%>
<% } -%>
res_hc
```

The call for `hierarchical_partition()`:

```{r, echo = FALSE}
print(res_hc@call)
```


Dimension of the input matrix:

```{r}
dim(res_hc@list[["0"]]@.env$data)
```

Global distribution for each sample:

```{r}
library(ComplexHeatmap)
densityHeatmap(res_hc@list[["0"]]@.env$data, anno = HeatmapAnnotation(df = res_hc@list[["0"]]@known_anno, 
	col = res_hc@list[["0"]]@known_col), ylab = "value")
```

About the hierarchy:


```{r}
max_depth = max_depth(res_hc)
max_depth
all_nodes = all_nodes(res_hc)
all_nodes
all_leaves = all_leaves(res_hc)
all_leaves
```


Partitions for different depth:

<% max_depth = max_depth(res_hc) -%>

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(depth in 2:max_depth) { -%>
knitr_add_tab_item('collect_classes(res_hc, depth = <%=depth%>)\nget_class(res_hc, depth = <%=depth%>)', 'depth = <%=depth%>')
<% } -%>
knitr_insert_tabs()
```

MDS plot:

```{r}
dimension_reduction(res_hc, merge = TRUE)
```

Or MDS plot at each node

<%
n_plots = length(setdiff(all_nodes(res_hc), all_leaves(res_hc)))
nc = min(c(4, n_plots))
nr = ceiling(n_plots/nc)
-%>

```{r, fig.width = <%=nc*14/3%>, fig.height = <%=nr*14/3%>, echo = 2}
par(mfrow = c(nr, nc))
dimension_reduction(res_hc, merge = FALSE)
par(mfrow = c(1, 1))
```

Signature genes and the overlap:

```{r, echo = max_depth > 2, eval = max_depth > 2}
lt_sig = get_signatures(res_hc)
venn_euler(lt_sig)
```


<% if(!is.null(res_hc@list[['0']]@known_anno)) {

Test correlation between subgroups and known annotations:

```{r, results = 'asis', echo = FALSE, include = TRUE}
<% for(depth in 2:max_depth) { -%>
knitr_add_tab_item('test_to_known_factors(res_hc, depth = <%=depth%>)', 'depth = <%=depth%>')
<%}-%>
knitr_insert_tabs()
```

-%>

## Results for each node

<%
is_hc = TRUE
for(node in setdiff(all_nodes(res_hc), all_leaves(res_hc))) { -%>
	<% brew(paste0(extdata_dir, "/section_template.Rmd")) %>
<%} -%>

## Session info

```{r}
sessionInfo()
```
