
---------------------------------------------------

<% 
if(is_hc) {
	mark = ""
	chunk_prefix = paste("node", node, sep = "-")
} else {
	tb = get_best_k(res_list)
	nm = paste(top_method, partition_method, sep = ":")
	mark = tb[nm, 5]
	chunk_prefix = paste(top_method, partition_method, sep = "-")
} -%>

<% if(is_hc) { %>
### Node <%=node%>
<% } else { %>
### <%=top_method%>:<%=partition_method%> <%=mark%>
<% } %>

The object which only contains results for a single top method and a single partition method,
and the functions that can be applied to.

```{r}
<% if(is_hc) { -%>
res = get_single_run(res_hc, node = "<%=node%>")
<% } else { -%>
res = get_single_run(res_list, top_method = "<%=top_method%>", partition_method = "<%=partition_method%>")
<% } -%>
res
```

Major plots made from `res` for different `k` (number of partitions). Individual plots can be found
later in this section.

```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] collect plots"))
```

```{r <%=chunk_prefix%>-collect-plots, fig.width = <%=fs*length(all_k)%>, fig.height = <%=fs*4%>, results = "hide"}
collect_plots(res)
```

Plots showing different statistics for choosing optimized `k`:

```{r <%=chunk_prefix%>-select-partition-number, results = "hide", fig.width = 10}
select_partition_number(res)
```

The values for different statistics for different `k`:

```{r}
get_stat(res)
```

Guess the best `k`:

```{r}
get_best_k(res)
```

The partitions:

```{r, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('get_class(res, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

Heatmaps for the consensus matrix:


```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] consensus heatmaps"))
```

```{r <%=chunk_prefix%>-consensus-heatmap, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('consensus_heatmap(res, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

Heatmaps for the membership of samples in each random sampling:


```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] membership heatmaps"))
```

```{r <%=chunk_prefix%>-membership-heatmap, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('membership_heatmap(res, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

Heatmaps for signatures:

```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] get signatures"))
```

```{r <%=chunk_prefix%>-signature, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('get_signatures(res, k = <%=k%>)', 'k = <%=k%>', opt = 'results = "hide"')
<%}-%>
knitr_insert_tabs()
```

```{r <%=chunk_prefix%>-signature-no-scale, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('get_signatures(res, k = <%=k%>, scale_rows = FALSE)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

Distribution of signatures in differnet subgroups:

```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] signature density"))
```

```{r <%=chunk_prefix%>-signature-density, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('signature_density(res, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

MDS plots:

```{r, echo = FALSE, message = FALSE}
message(qq("  [@{top_method}:@{partition_method}] MDS plots"))
```

```{r <%=chunk_prefix%>-mds, results = "asis", echo = FALSE, include = TRUE}
<% for(k in all_k) { -%>
knitr_add_tab_item('dimension_reduction(res, k = <%=k%>)', 'k = <%=k%>')
<%}-%>
knitr_insert_tabs()
```

How subgroups split when increasing `k`:

```{r <%=chunk_prefix%>-collect-classes}
collect_classes(res)
```

<% if(!is.null(res_list@list[[1]]@known_anno)) { %>
	
Test to known annotations:

```{r, eval = !is.null(res@known_anno), echo = !is.null(res@known_anno)}
test_to_known_factors(res)
```

<%}-%>


Consider to use `submit_to_david()` to do function enrichment for each signature list.
