
---------------------------------------------------

### @{node}


The object which only contains results for a single top method and a single partition method,
and the functions that can be applied to.

```{r}
res = get_single_run(res_hc, node = "@{node}")
res
```

Major plots made from `res` for different `k` (number of partitions). Individual plots can be found
later in this section.

@{
k = res_hc@list[['0']]@k
nk = length(k)
fs = min(c(3*nk, 14))/nk
""
}

```{r @{node}-collect-plots, fig.width = @{fs*nk}, fig.height = @{fs*4}, results = "hide"}
collect_plots(res)
```

Plots showing different statistics for choosing optimized `k`:

```{r @{node}-select-partition-number, results = "hide", fig.width = 10}
select_partition_number(res)
```

The values for different statistics for different `k`:

```{r}
get_stat(res)
```

Guess the best `k`:

```{r}
get_best_k(res)
```

The partitions:

```{r, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('get_class(res, k = @<k>)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

Heatmaps for the consensus matrix:

```{r @{node}-consensus-heatmap, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('consensus_heatmap(res, k = @<k>)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

Heatmaps for the membership of samples in each random sampling:

```{r @{node}-membership-heatmap, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('membership_heatmap(res, k = @<k>)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

Heatmaps for signatures:

```{r @{node}-signature, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('get_signatures(res, k = @<k>)', 'k = @<k>', opt = 'results = \"hide\"')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

```{r @{node}-signature-no-scale, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('get_signatures(res, k = @<k>, scale_rows = FALSE)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

Distribution of signatures in differnet subgroups:

```{r @{node}-signature-density, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('signature_density(res, k = @<k>)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

MDS plots:

```{r @{node}-mds, results = "asis", echo = FALSE, include = TRUE}
@{ k = res_hc@list[['0']]@k
qq("knitr_add_tab_item('dimension_reduction(res, k = @<k>)', 'k = @<k>')\n", code.pattern = "@<CODE>") }
knitr_insert_tabs()
```

How subgroups split when increasing `k`:

```{r @{node}-collect-classes}
collect_classes(res)
```

@{if(!is.null(res_hc@list[['0']]@known_anno)) "Test to known annotations:\n" else ""}

```{r, eval = !is.null(res@known_anno), echo = !is.null(res@known_anno)}
test_to_known_factors(res)
```


Consider to use `submit_to_david()` to do function enrichment for each signature list.
