<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{1. A Quick Start of cola Package}
-->

A Quick Start of cola Package
=============================================================

**Author**: Zuguang Gu ( z.gu@dkfz.de )

**Date**: `r Sys.Date()`

**Package version**: `r installed.packages()["cola", "Version"]`

-------------------------------------------------------------

```{r, echo = FALSE, message = FALSE}
library(markdown)
library(knitr)
knitr::opts_chunk$set(
    error = FALSE,
    tidy  = FALSE,
    message = FALSE,
    fig.align = "center")
options(width = 100)
library(cola)
```

Assume your matrix is stored in an object called `mat`, to perform consensus
partitioning with *cola*, you only need to run following code:

```{r, eval = FALSE}
# code only for demonstration
mat = adjust_matrix(mat)  # optional
rl = run_all_consensus_partition_methods(mat, mc.cores = ...)
cola_report(rl, output_dir = ..., mc.cores = ...)
```

In above code, there are three steps:

1. Adjust the matrix. In this step, rows with too many `NA`s are removed. Rows
   with very low variance are removed. `NA` values are imputed if there are
   not too many in each row. Outliers are adjusted in each row. This step is
   partition methods are `hclust` (hierarchical clustering with cutree),
   `kmeans` (k-means clustering), `skmeans::skmeans` (spherical k-means
   clustering), `cluster::pam` (partitioning around medoids clustering) and
   `Mclust::mclust` (model-based clustering). The default methods to extract
   top n rows are `SD` (standard deviation), `CV` (coefficient of variation),
   `MAD` (median absolute deviation) and `ATC` (ability to correlate to other
   rows). 
3. Generate a detailed HTML report for the complete analysis.

There are examples on real datasets for _cola_ analysis that can be found at https://jokergoo.github.io/cola_collection/.
